Automated verification of stand-alone solar photovoltaic systems

### 2018-11-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

In order to model, simulate or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan}, \cite{Swarnkar}, \cite{NRELDobos}, \cite{NRELBlair}, \cite{Mills}. And even general purpose simulation tools as PSpice, Saber or MATLAB/Simulink package \cite{Gow1999}, \cite{Benatiallah2017}.

@@

Formal methods based on software model checking offer great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.  
%with behavior that is, in principle, well determined. 
 Using this technique, any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the program meets its specification. User or project requirements can be added during the process of coding. %, as defined by \cite{Trindade}. 
%
%This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
% Their aim is to establish system correctness with mathematical rigor. 
%In the recent decades, research in formal methods has led to the development of very promising verification techniques.
% that facilitate the early detection of bugs in order to ensure the correctness of the system. 
%
%Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
%Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}. 
Finally, model checking algorithms can verify the system model by systematically exploring all their states. That way, the formal proof can verify if the requirements are met by the system.

Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}. It allows one to develop models for each component of the system. At this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load are created. The behavior of each system can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself. A key benefit to this approach is that it helps in the detection of faults and flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}.

%Those programs are viewed as mathematical objects, and the use of 
%Bringing this technique to solar PV systems, i
%Instead of finding a bug or a software inconsistence, t
%Here it will be verified a stand-alone PV system, with all their components modeled mathematically, 
Related to solar PV systems, the project requirements, as battery autonomy and power demand, beside weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process. The model checking tool reports in which conditions a system does not meet the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.

%Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC), which allows one to formally verify a PV system as a C program.

In most prior studies, the evaluation of PV systems, concerning the meeting of user requirements, were performed by software simulation tools using MATLAB/Simulink \cite{Benatiallah2017}, \cite{Samrat2014}, and \cite{Natsheh2012} or HOMER Pro \cite{Lamnadi2017}. Some studies were carried out toward the formal modeling of power smart grids \cite{Akram2018}, and to maximize the power point of solar panels \cite{Driouich2017}; however, those studies do not perform automated verification and they restrict themselves to solar panels or smart grids.

In addition, recent research that applies formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels, where the focus have been on the modeling of the dynamics of PV panels and their interaction with the grid, without batteries~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}. Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.

%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool. 
To the best of our knowledge, this is the first initiative to use a verification tool to evaluate a stand-alone solar PV systems. %, with weather conditions variation. 
The mains contribution of this paper are the automated verification of the PV system, and the modular modeling of each component of the PV system, which allows one to change the mathematical models, besides changing the type of energy generation in the future to another renewable source.

@@

\textit{Outline}. Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling. Section~\ref{sec:AutomatedVerification} presents the automated verification technique. The methodology is presented at section~\ref{sec:Methodology}. Section~\ref{sec:results} is devoted to the results. Section~\ref{sec:Conclusions} presents the conclusion and describes future work.

>>>>

In order to model, simulate, or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan}, \cite{Swarnkar}, \cite{NRELDobos}, \cite{NRELBlair}, \cite{Mills}; and even general purpose simulation tools as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999}, \cite{Benatiallah2017}.

@@

Formal methods based on software model checking offer great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.  
%with behavior that is, in principle, well determined. 
 Using this technique, any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the program meets its specification. User or project requirements can be added during the process of coding. %, as defined by \cite{Trindade}. 
%
%This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
% Their aim is to establish system correctness with mathematical rigor. 
%In the recent decades, research in formal methods has led to the development of very promising verification techniques.
% that facilitate the early detection of bugs in order to ensure the correctness of the system. 
%
%Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
%Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}. 
Finally, model checking algorithms can verify the system model by systematically exploring all their states. As a result, the formal proof can verify if the requirements are met by the system.

Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}. It allows one to develop models for each component of the system. In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load are created. The behavior of each system can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself. A key benefit to this approach is that it helps in the detection of faults and flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}.

%Those programs are viewed as mathematical objects, and the use of 
%Bringing this technique to solar PV systems, i
%Instead of finding a bug or a software inconsistence, t
%Here it will be verified a stand-alone PV system, with all their components modeled mathematically, 
Related to solar PV systems, the project requirements, as battery autonomy and power demand, beside weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process. The model checking tool reports in which conditions a system does not meet the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.  
%Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}, which allows one to formally verify a PV system as a C program.

In prior studies, the evaluation of PV systems, concerning the meeting of user requirements, were performed by software simulation tools using MATLAB/Simulink \cite{Benatiallah2017}, \cite{Samrat2014}, and \cite{Natsheh2012} or HOMER Pro \cite{Lamnadi2017}. Some studies were carried out toward the formal modeling of power smart grids \cite{Akram2018}, and to maximize the power point of solar panels \cite{Driouich2017}; however, those studies do not perform automated verification and they restrict themselves to solar panels or smart grids.

In addition, recent research that applies formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels, where the focus has been on the modeling of the dynamics of PV panels and their interaction with the grid, without batteries~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}. Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.

%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool. 
Given the current knowledge in formal verification, this is the first initiative to use a verification tool to evaluate a stand-alone solar PV systems. %, with weather conditions variation. 
The mains contribution of this paper are the automated verification of the PV system, and the modular modeling of each component of the PV system, which allows one to change the mathematical models, besides changing the type of energy generation in the future to another renewable source.

@@

\textit{Outline}. Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling. Section~\ref{sec:AutomatedVerification} presents the automated verification technique. The methodology is presented in section~\ref{sec:Methodology}. Section~\ref{sec:results} is devoted to the results. Section~\ref{sec:Conclusions} presents the conclusion and describes future work.
